30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-18 paper.tex
Fixes for onion routing section

		After node $X$ receives this packet from out trusted node $C$, it decrypts the attached secret with its private key, and uses that secret to decrypt the rest of the packet. The result is a header with the address for node $Y$ and the payload encrypted with secrets for the following nodes in the circuit, which is forwarded to node $Y$.

>>>>

		After node $X$ receives this packet from our trusted node $C$, it decrypts the attached secret with its private key, and uses that secret to decrypt the rest of the packet. The result is a header with the address for node $Y$ and the payload encrypted with secrets for the following nodes in the circuit, which is forwarded to node $Y$.
